\textls[-0]{\thetitle}

### 2023-03-04 metatheory-condensed.tex
reply to a comment

In dependent type system, types are treated as terms, and should have a type. \rA{Why is W(t) a term and not a type?}\EDJreply{changed, please review.}
We use Tarski-style universes~\cite{hofmann1997syntax}: every type has a \emph{code}, inhabits in a universe~$\cU$,
with $\El{t}$ decoding~$t$ (rule \ruleref{ty/el})
and $\codety{T}$ encoding type~$T$ (rule \ruleref{tm/c}).
MLTT has an infinite hierarchy of universes;
we omit universe levels in the presentation for conciseness.

>>>>

%In dependent type system, types are treated as terms, and should have a type.
We use Tarski-style universes~\cite{hofmann1997syntax}:
a universe~$\cU$ is not inhabited by types directly,
but rather by the \emph{codes} of types:
$\codety{T}$ encodes type~$T$ (rule \ruleref{tm/c}),
and $\El{t}$ decodes~$t$ (rule \ruleref{ty/el}).
MLTT has an infinite hierarchy of universes;
we omit universe levels in the presentation for conciseness.
\rA{Why is W(t) a term and not a type?}\EDJreply{changed, please review.}\YZreply{I think the reviewer is wondering what is gained by encoding and decoding types, compared to types directly inhabiting universes.}
